### 2019-01-12 paper/main copy.tex
Added paper

\PassOptionsToPackage{usenames}{xcolor}
\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass{llncs}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{url}
\usepackage{xspace}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{color}
\usepackage{boxedminipage}
\usepackage[ff,sets,keys,primitives,operators]{cryptocode}
\usepackage{framed}
\usepackage[group-separator={,}]{siunitx}
\newcommand\bmmax{2}
\usepackage{bm}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{footnote}
\usepackage{units}
\usepackage{multicol,lipsum}
\colorlet{iomsg}{MidnightBlue}
\colorlet{party}{brown}
\colorlet{entry}{NavyBlue}
\colorlet{string}{BlueViolet}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\instantiated}{\mathsf{instantiated}}
\newcommand{\instantiatedno}{\mathsf{NO}}
\newcommand{\instantiatedyes}{\mathsf{YES}}

\newcommand{\gamestatus}{\mathsf{phase}}
\newcommand{\gameregister}{\mathsf{INIT}}
\newcommand{\gamesetup}{\mathsf{SETUP}}
\newcommand{\gameattack}{\mathsf{ATTACK}}
\newcommand{\gamereveal}{\mathsf{REVEAL}}
\newcommand{\gamewinner}{\mathsf{WIN}}
\newcommand{\gamefraud}{\mathsf{FRAUD}}
\newcommand{\gamefinished}{\mathsf{GAMEOVER}}

\newcommand{\chanstatus}{\mathsf{status}}

\newcommand{\chanon}{\mathsf{ON}}
\newcommand{\chandispute}{\mathsf{DISPUTE}}
\newcommand{\chanoff}{\mathsf{OFF}}

\newcommand{\hready}{\mathsf{hready}}
\newcommand{\hboard}{\mathsf{hboard}}
\newcommand{\hcell}{\mathsf{hcell}}
\newcommand{\hship}{\mathsf{hship}}
\newcommand{\hshiplocation}{\mathsf{hshiplocation}}

%\newcommand{\hash}{\textsf{H}}
\newcommand{\cmd}{\mathsf{cmd}}
\newcommand{\inputs}{\mathsf{inputs}}
\newcommand{\hstate}{\mathsf{hstate}}
\newcommand{\hstatei}{\mathsf{hstate}_{\monotoniccounter}}
\newcommand{\hstateplus}{\ensuremath{\mathsf{hstate}_{\monotoniccounter+1}}}
\newcommand{\hstateminus}{\ensuremath{\mathsf{hstate}_{\monotoniccounter-1}}}
\newcommand{\monotoniccounter}{\mathsf{i}}
\newcommand{\stateinfo}{\mathsf{state}}
\newcommand{\stateinfoi}{\mathsf{state}_{\mathsf{i}}}
\newcommand{\stateinfominus}{\mathsf{state}_{\mathsf{i-1}}}
\newcommand{\stateinfoplus}{\mathsf{state}_{\mathsf{i+1}}}
\newcommand{\participant}{\mathcal{P}}

\newcommand{\rani}{\mathsf{r}_{\mathsf{i}}}
\newcommand{\ran}{\mathsf{r}}
\newcommand{\ranminus}{\mathsf{r}_{\mathsf{i-1}}}
\newcommand{\ranplus}{\mathsf{r}_{\mathsf{i+1}}}

\newcommand{\statechannel}{\mathsf{SC}}
\newcommand{\statechanneldispute}{\mathsf{SC}.\mathsf{trigger}}
\newcommand{\statechannelsetstate}{\mathsf{SC}.\mathsf{setstatehash}}
\newcommand{\statechannelresolve}{\mathsf{SC}.\mathsf{resolve}} 
\newcommand{\statechannelgetcommitment}{\mathsf{SC}.\mathsf{getstatehash}} 
\newcommand{\statechannelgetdispute}{\mathsf{SC}.\mathsf{getdispute}} 
\newcommand{\statechannelclose}{\mathsf{SC}.\mathsf{close}}

\newcommand{\sign}{\mathsf{Sign}}
\newcommand{\verifysig}{\mathsf{VerifySig}}

\newcommand{\battleship}{\mathsf{BS}}
\newcommand{\battleshipfraud}{\mathsf{BS.fraud}}
\newcommand{\battleshipattackcell}{\mathsf{BS.attackcell}}
\newcommand{\battleshipbegin}{\mathsf{BS.begingame}}
\newcommand{\battleshipquit}{\mathsf{BS.quitgame}}
\newcommand{\battleshipcommit}{\mathsf{BS.commit}}
\newcommand{\battleshipplacebet}{\mathsf{BS.placebet}}
\newcommand{\battleshipselectboard}{\mathsf{BS.select}}
\newcommand{\battleshiprevealcell}{\mathsf{BS.opencell}}
\newcommand{\battleshipsinking}{\mathsf{BS.sunk}}
\newcommand{\battleshiprevealships}{\mathsf{BS.openships}}
\newcommand{\battleshiprevealboard}{\mathsf{BS.openships}}
\newcommand{\battleshipgameover}{\mathsf{BS.gameover}}
\newcommand{\battleshipdeposit}{\mathsf{BS.deposit}}
\newcommand{\battleshipwithdraw}{\mathsf{BS.withdraw}}
\newcommand{\battleshipfinish}{\mathsf{BS.finish}}

%\newcommand{\battleshipshipnotplaced}{\mathsf{BS.fraudnothit}}
\newcommand{\battleshipdeclarednotsunk}{\mathsf{BS.declarednotsunk}}
\newcommand{\battleshipdeclarednothit}{\mathsf{BS.declarednothit}}
\newcommand{\battleshipsamecell}{\mathsf{BS.attacksamecell}}
\newcommand{\battleshiptwoships}{\mathsf{BS.celltwoships}}
\newcommand{\battleshipchallengeexpired}{\mathsf{BS.expiredchallenge}}

\newcommand{\battleshiplock}{\mathsf{BS.lock}}
\newcommand{\battleshipunlock}{\mathsf{BS.unlock}}
\newcommand{\battleshipgetstate}{\mathsf{BS.getstate}}

\newcommand{\appcontract}{\mathsf{AC}}
\newcommand{\applock}{\mathsf{AC.lock}}
\newcommand{\appunlock}{\mathsf{AC.unlock}}

\newcommand{\timerchallenge}{\mathsf{\Delta}_{\mathsf{challenge}}}
\newcommand{\timechallenge}{\mathsf{t}_{\mathsf{challenge}}}
\newcommand{\timerextra}{\mathsf{\Delta}_{\mathsf{extra}}}
\newcommand{\timerdispute}{\mathsf{\Delta}_{\mathsf{dispute}}}
\newcommand{\timenow}{\mathsf{t}_{\mathsf{now}}}
\newcommand{\timestart}{\mathsf{t}_{\mathsf{start}}}
\newcommand{\timeend}{\mathsf{t}_{\mathsf{end}}}
\newcommand{\timedispute}{\timenow + \mathsf{\Delta}_{\mathsf{dispute}}}

\newcommand{\appblue}{\textcolor{entry}{\bf AC}}
\newcommand{\chanblue}{\textcolor{entry}{\bf SC}}
\newcommand{\depositblue}{\textcolor{entry}{\bf deposit}}
\newcommand{\timeoutblue}{\textcolor{entry}{\bf timeout}}
\newcommand{\transitionblue}{\textcolor{entry}{\bf transition}}
\newcommand{\resolveblue}{\textcolor{entry}{\bf resolve}}
\newcommand{\setstateblue}{\textcolor{entry}{\bf setstate}}
\newcommand{\chanchallenge}{\textcolor{entry}{\bf challenge}}
\newcommand{\triggerdispute}{\textcolor{entry}{\bf triggerDispute}}
\newcommand{\assertstate}{\textcolor{entry}{\bf assertState}}
\newcommand{\getbalance}{\textcolor{entry}{\bf getBalance}}
\newcommand{\DEPOSIT}{\texttt{DEPOSIT}}
\newcommand{\DISPUTE}{\texttt{DISPUTE}}
\newcommand{\ON}{\texttt{ON}}
\newcommand{\hashblue}{\textcolor{entry}{\bf hash}}

% Colorful diagrams 
\newcommand{\contract}{\textcolor{entry}{\bf contract }}
\newcommand{\constructor}{\textcolor{entry}{\bf constructor }}
\newcommand{\oninput}{\textcolor{entry}{\bf function }}
\newcommand{\view}{\textcolor{entry}{\bf view}}
\newcommand{\pure}{\textcolor{entry}{\bf pure}}
\newcommand{\internal}{\textcolor{entry}{\bf internal}}
\newcommand{\public}{\textcolor{entry}{\bf public}}
\newcommand{\bytes}{\textcolor{entry}{\bf bytes}}
\newcommand{\memory}{\textcolor{entry}{\bf memory}}
\newcommand{\storage}{\textcolor{entry}{\bf storage}}
\newcommand{\addr}{\textcolor{entry}{\bf address}}
\newcommand{\uinteight}{\textcolor{entry}{\bf uint8}}
\newcommand{\uint}{\textcolor{entry}{\bf uint256}}
\newcommand{\uintno}{\textcolor{entry}{\bf uint}}
\newcommand{\intno}{\textcolor{entry}{\bf int}}
%\newcommand{\bytes}{\textcolor{entry}{\bf bytes}}
\newcommand{\strings}{\textcolor{entry}{\bf string}}
\newcommand{\struct}{\textcolor{entry}{\bf struct}}
\newcommand{\returns}{\textcolor{entry}{\bf returns}}
\newcommand{\stringlitt}[1]{\texttt{\textcolor{string}{#1}}}
\newcommand{\comment}[1]{\texttt{\textcolor{OliveGreen}{#1}}}
\newcommand{\byte}{\textcolor{entry}{\bf byte}}
\newcommand{\byteone}{\textcolor{entry}{\bf byte1}}
\newcommand{\bytetwo}{\textcolor{entry}{\bf bytetwo}}
\newcommand{\bytethreetwo}{\textcolor{entry}{\bf bytes32}}
\newcommand{\bool}{\textcolor{entry}{\bf bool}}
\newcommand{\event}{\textcolor{entry}{\bf event}}
\newcommand{\emit}{\textcolor{entry}{\bf emit}}
\newcommand{\modifier}{\textcolor{entry}{\bf modifier}}
\newcommand{\require}{\textcolor{entry}{\bf require}}
\newcommand{\assert}{\textcolor{entry}{\bf assert}}
\newcommand{\revert}{\textcolor{entry}{\bf revert}}
\newcommand{\payable}{\textcolor{entry}{\bf payable}}
\newcommand{\ifs}{\textcolor{entry}{\bf if}}
\newcommand{\elses}{\textcolor{entry}{\bf else}}
\newcommand{\for}{\textcolor{entry}{\bf for}}
\newcommand{\dos}{\textcolor{entry}{\bf do}}
\newcommand{\whiles}{\textcolor{entry}{\bf while}}
\newcommand{\mapping}{\textcolor{entry}{\bf mapping}}
\newcommand{\enum}{\textcolor{entry}{\bf enum}}
\newcommand{\msgsender}{\textcolor{entry}{\bf msg.sender}}
\newcommand{\block}{\textcolor{entry}{\bf block}}
\newcommand{\tx}{\textcolor{entry}{\bf tx}}
\newcommand{\msg}{\textcolor{entry}{\bf msg}}
\newcommand{\gasprice}{\textcolor{entry}{\bf gasprice}}
\newcommand{\origin}{\textcolor{entry}{\bf origin}}
\newcommand{\gasleft}{\textcolor{entry}{\bf gasleft()}}
\newcommand{\values}{\textcolor{entry}{\bf value}}
\newcommand{\balance}{\textcolor{entry}{\bf balance}}
\newcommand{\transfer}{\textcolor{entry}{\bf transfer}}
\newcommand{\send}{\textcolor{entry}{\bf send}}
\newcommand{\this}{\textcolor{entry}{\bf this}}
\newcommand{\coinbase}{\textcolor{entry}{\bf coinbase}}
\newcommand{\gaslimit}{\textcolor{entry}{\bf gaslimit}}
\newcommand{\numbers}{\textcolor{entry}{\bf number}}
\newcommand{\timestamp}{\textcolor{entry}{\bf timestamp}}
\newcommand{\blockhash}{\textcolor{entry}{\bf blockhash}}
\newcommand{\shatwo}{\textcolor{entry}{\bf sha256}}
\newcommand{\shathree}{\textcolor{entry}{\bf keccak256}}
\newcommand{\abiencode}{\textcolor{entry}{\bf abi.encodePacked}}
\newcommand{\ecrecover}{\textcolor{entry}{\bf ecrecover}}
\begin{document}

	\title{2 Party State Assertion Channels }

	\author{Chris Buckland and Patrick McCorry}

	\institute{Kings College London, UK\\
		\email{patrick.mccorry@kcl.ac.uk}}

	\maketitle
	\begin{abstract}
	%State channels are a scaling technique for cryptocurrencies as it lets a group of parties execute a smart contract locally amongst themselves instead of the global network. 
	%In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
	%If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute which appoints the blockchain as an arbitrator to resolve it. 
	An empirical case study to evaluate state channels as a scaling solution for cryptocurrencies demonstrated that providing an application's full state during the dispute process for a state channel is financially costly (i.e. \$1.5 to \$57.57 for a battleship game) which can hamper their real-world use. 
	To overcome this issue, we present \emph{State Assertion Channels}, the first state channel to guarantee  an honest party is always refunded the cost if it becomes necessary to send an application's full state during the dispute process. 
	Furthermore it ensures an honest party will pay an approximate fixed cost to continue an application's execution via the dispute process. 
	We provide a proof of concept implementation which demonstrates it costs approximately \$x to submit evidence  regardless of the smart contract's application.

	\end{abstract}

\section{Introduction}

Cryptocurrencies do not scale.
The community are pursing three approaches to alleviate the scalability issue which includes new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols. 
While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as it reduces  the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable. 
This paper focuses on the off-chain (or so-called Layer 2) approach that simply aims to reduce the network's load.
One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of the global network. 
In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
If there is a disagreement about the latest state of the smart contact, then any party can trigger a dispute and rely on the underlying blockchain to arbitrate the dispute's outcome.
To arbitrate, the blockchain provides a fixed time period to collect evidence from all online parties before using this evidence to decide the off-chain smart contract's new state. 
So far, there are two types of dispute processes for a state channel. 
The first is a \emph{closure dispute} \cite{statechannelnetworks,battleship,celernetwork} as the dispute process is responsible for closing the channel, re-deploying the smart contract with the new state and letting parties continue its execution via the blockchain. 
The second is a \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual} as the dispute process collects commands from each party and then executes the command to compute the new state. 
A recent case study empirically evaluated state channels as a scaling solution by building the  two player game battleship \cite{battleship}.
They highlighted the most expensive aspect of any dispute process is sending the application's full state. 
For example, the  case study claimed that sending the full game state approximately costs \$1.57 when the blockchain is not congested, but it can potentially sky-rocket to \$57.57 if the blockchain is congested. 
The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution). 
We propose, \emph{State Assertion Channels}, which has a command-issuance dispute process\footnote{The assertion concept isn't compatible with closure channels as the full state is required to re-deploy an application.}.  and overcomes the issue of sending the application's full state by leveraging the concept of an optimistic contract.
Our contributions:

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the applicaton's full state during the dispute proess.  
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}

\section{Background}

\paragraph{Optimistic Smart Contracts }

An optimistic smart contract trades the cost of computation with time.
This lets a smart contract accept an application's new state if no one has proved it is invalid within a fixed challenge period. 
Briefly, one party submits the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
Thi asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
Other interested parties can compute the transition locally to verify its validity.
If the asserted state is invalid, then anyone can issue a challenge by notifying the smart contract to compute the transition.
If the challenge is successful, then the bond is used to refund the challenger. 
Eigenmann, Moore and Johnson provided the first implementation of an optimistic contract for the Ethereum Name Service
\cite{optimisticcontracts}, but so far this technique has alluded real-world use.

\paragraph{Command Issuance State Channels}
Sprites proposed the concept of a command-issuance state channel, and since then it has been extended by PISA \cite{mccorry2018pisa}, Counterfactual \cite{coleman2018counterfactual} and Magmo \cite{magmo}. 
At a high level, one party can submit the latest $\stateinfoi$ agreed by all parties before triggering the dispute process.
The smart contract provides a fixed time period for all parties to submit commands and the contract is responsible for computing every command (i.e. state transition).
In Sprites (and PISA), all commands are executed after the dispute process has expired.
Whereas in Counterfactual and Magmo, the command is executed when it is submited and the dispute period's expiry time is reset (i.e. it dispute period is extended for every command). 
The dispute process can be cancelled if one party submits a later state agreed by all parties, or after the expiry time.

\section{State Assertion Channels}
We provide a high level overview of state assertion channels to show how it combines optimistic contracts and command issuance channels.
Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
Finally we'll present the state assertion channel contract $\chanblue$ and the interaction amongst both parties, $\chanblue$ and $\appblue$.

\subsection{High level overview}

The state assertion contract $\chanblue$ and the application contract $\appblue$ must be deployed on the blockchain.
Each party must lock coins into the state channel before they can begin co-operatively executing the application off-chain amongst themselves. 
If there is a disagreement off-chain, then both parties can continue its progression via the dispute process.
Our contribution involves changing the dispute process to avoid sending the full application's state.
Instead parties will assert an application's new state by submitting a hash of the previous state $\hstatei$, the command $\cmd$, its $\inputs$, a hash of the next state $\hstateplus$ and a financial \texttt{bond}. 
%This asserts that $\hstateplus$ represents the application's new state if the command (and its input) was executed by $\appblue$. 
The dispute process provides a fixed time period for the counterparty to verify the assertion by computing the state transition locally. 
To challenge an assertion, the party submits the previous $\stateinfominus$ which lets $\chanblue$ verify the assertion was indeed correct by executing the transition via $\appblue$.  
If the honest party successfully challenges an assertion and proves it is invalid, then they are sent the \texttt{bond} as a refund.
Thus an honest party can always continue an applicaton's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.

\subsection{Application Contract Assumptions} \label{sec:assumptions}

\paragraph{Turn-based application} 
We assume it is a turn-based application and each party performs their state transition in turn. 
As well, $\appblue$ must be instantiated on the blockchain to ensure its address is provided to the  state assertion contract $\chanblue$.

\paragraph{Single transition function} 
The application contract implements a transition function which accepts the full state, a command and a list of inputs.
The application contract is responsible for computing a state transition and returning a hash of the new state via 
$	\hstateplus := \texttt{Transition}(\stateinfoi, \cmd, \inputs); $.
The application contract is stateless and the state must be supplied to compute a state transition.

\paragraph{No exceptions or out-of-gas errors} 
The application's transition function must return a hash of the state $\hstate$.
If the command doesn't exist or its execution simply fails, then it should return $\hstate = 0$. 
This ensures $\chanblue$ can always verify a state assertion's validity.
If out-of-gas exceptions were permitted by an application, then it can be leveraged to prevent an honest user challenging it (i.e. $\chanblue.\chanchallenge()$'s execution will never complete).

\subsection{Assertion Channel Overview} 
Figure \ref{fig:fallback} presents the state channel assertion contract.
We'll use it to aid the following overview on how to instantiate the contract, authorise states off-chain, how to trigger a dispute, how to submit and challenge assertions, and finally how to close the channel.

\paragraph{Channel status} 
The channel has three flags $\texttt{Status} = \{\DEPOSIT, \ON, \DISPUTE\}$. 
Both parties must deposit coins in $\chanblue$ before it will transition from $\DEPOSIT \rightarrow \ON$.  
While the channel's status is set as $\ON$ both parties can co-operatively continue the application's progression off-chain by exchanging signatures for new states.
If there is a disagreement about a state transition, then one party can trigger a dispute which changes the status from $\ON \rightarrow \DISPUTE$. 
The contract self-enforces a turn-based dispute process.
One party asserts a new state, and the other party can either challenge it by notifying the contract to check the state transition, or they can approve it by asserting a new state which extends it. 
The dispute process can only finish and let the status change from $\DISPUTE \rightarrow \ON$ if one party submits a co-operatively signed new state.

\paragraph{Instantiating contract} 
One party must deploy $\chanblue$ to the blockchain and initalise it with the address of both parties $\participant_{1},\participant_{2}$, the application's address $\appblue$, the fixed dispute period $\Delta$ and the required security bond $\texttt{bond}$. 
Both parties must review the contracts $\chanblue,\appblue$ and the intialisation values before sending their deposit via $\chanblue.\depositblue()$.
After $\chanblue$ has received both deposits (and before turning on the channel), it will compute the initial state $\stateinfo_\texttt{initial} =$ ($\bot$,\texttt{balance1},\texttt{balance2}) and declare the first turn will be taken by $\participant_{1}$.\footnote{We highlight a subtle difference between the initial state ($\bot$,\texttt{balance1},\texttt{balance2}) and the terminal state  (\texttt{balance1},\texttt{balance2}).}

\paragraph{Progressing application off-chain} 
Both parties can begin exchanging signatures to execute the application off-chain when the channel is $\ON$. 
In each round, one party is responsible for proposing a state transition, and the other party is responsible for verifying the state transition before co-operatively authorising it. 
To propose, the party computes $\stateinfoplus = \texttt{Transition}(\stateinfoi, \inputs, \cmd)$, they hash the state $\hstateplus = \texttt{hash}(\stateinfoplus)$ and they sign its hash $\sigma_{\participant_{1}} = \sign(\hstateplus, \monotoniccounter+1, \chanblue, \participant_{\texttt{turn}})$, where $\participant_{\texttt{turn}}$ specifies the next party's turn. 
The proposer must send $\hstateplus, \monotoniccounter+1, \sigma_{\participant}$ to the counterparty. 
To verify, the counterparty computes state transition and the state hash $\hstateplus'$ before checking if $\hstateplus' == \hstateplus$. 
If this condition is satisified (and $\monotoniccounter+1$ is the largest counter so far), then the counterparty signs 
$\sigma_{\participant_{2}} = \sign(\hstateplus, \monotoniccounter+1, \chanblue, \participant_{\texttt{turn}})$ and sends their signature $\sigma_{\participant_{1}}$ to the proposer.

\paragraph{Triggering a dispute} 
In general, a dispute must be triggered if the counterparty stops honestly following the protocol (i.e. aborts and stops responding) and there are two cases to consider.
Either the proposer is waiting on a signature from the verifier to authorise the new state, or the verifier is waiting on the proposer to propose a new state transition. 
In both cases, each party waits for a local time-out before submiting the most recently $\hstatei$ via $\chanblue.\setstateblue()$ and triggering a dispute via $\chanblue.\triggerdispute()$. 
The signed state hash includes $\participant_{\texttt{turn}}$ and thus $\chanblue$ waits for a new state assertion from the named party before $\texttt{deadline} = \texttt{now} + \Delta$.
To continue off-chain and cancel the dispute, one party must submit a co-operatively signed $\hstate$ (with a larger counter $\monotoniccounter$) via $\chanblue.\setstateblue$.

\paragraph{Submitting a state assertion} 
The named party $\participant_{\texttt{turn}}$ must send an asserted  $\hstateplus$, the command $\cmd$ and its inputs $\inputs$ using $\chanblue.\assertstate()$ before the dispute process expiry time $\texttt{deadline}$. 
Every time a state assertion $\hstateplus$ is submitted, the contract resets the deadline $\texttt{deadline} = \texttt{now} + \Delta$ and stores the previous state assertion $\hstatei$ as accepted. 
Furthermore the contract records that it is the counterparty's turn to respond.
In terms of the financial bond, the contract only needs to store a single \texttt{bond} per party which can be collected when the party asserts a new state or when the parties send their initial deposit.

\paragraph{Responding to a state assertion} 
The counterparty is responsible for verifying if a state assertion is correct by computing $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$ locally and checking if the asserted $\hstateplus$ represents $\stateinfoplus$. 
If the state assertion is valid, then the counterparty can continue the application's execution by responding with a new state assertion using $\chanblue.\assertstate()$.
By continuing the application's execution, the counterparty is agreeing that the previous state assertion is valid. 
If the state assertion is invalid, then the counterparty can challenge it by supplying the plaintext state $\stateinfoi$ to the contract using $\chanblue.\chanchallenge()$. 
The contract will compute the transition and confirm if $\hstateplus$ represents the new state $\stateinfoplus$. 
If the challenger is successful and proves the state assertion as invalid, they are sent all coins in the channel (including the counterparty's \texttt{bond} to refund the cost of this transaction).

\paragraph{Reaching the terminal state}

In Section \ref{sec:assumptions}, we assumed an application's execution will always reach a terminal state which is simply the final balance of both parties $\stateinfo_{\texttt{final}}$ = (\texttt{balance1},\texttt{balance2}).
%and both parties will be sent their respective final balance (alongside their security bonds) if the state is submitted to the contract using $\chanblue.\resolveblue()$. 
The final  $\hstate_{\texttt{final}}$ must be accepted by the assertion contract $\chanblue$ before both parties are sent their final balance by supplying  $\stateinfo_{\texttt{final}}$ to $\chanblue.\resolveblue()$. 
It is clear if both parties continue the application's execution co-operatively off-chain, then they can simply send the terminal state hash via $\chanblue.\setstateblue()$ before resolving the channel. 
On the other hand, the dispute process enforces turn-based state assertions to ensure that one party will eventually propose the terminal state hash via $\chanblue.\assertstate()$. 
When the terminal state hash is reached, the counterparty's only option is to submit  $\stateinfo_{\texttt{final}}$ before the deadline using $\chanblue.\resolveblue()$

\section{Discussion and Future Work}

%\paragraph{Proof of concept implementation} 
%Table 1 outlines the gas costs for creating the state channel smart contract and its dispute process. 
%As we can see creating the smart contract costs x, and the entire dispute process for a single state assertion costs x. 
%

\paragraph{Honest party can always verify a state transition} 
%An honest party can only challenge a state assertion if they have a copy of the previous $\stateinfo$.
There are only two opportunities for a new state hash to be accepted by $\chanblue$. 
%Thus the honest party must have the previous state in plaintext as they must verify the state transition before accepting it.
The first opportunity requires one party to submit the state hash via $\chanblue.\setstateblue()$ which requires both parties to have already signed it. 
The second opportunity requires one party to submit $\hstatei$ via $\chanblue.\assertstate()$ and for the honest party to continue the application's execution by asserting the next $\hstateplus$ via $\chanblue.\assertstate()$. 
The contract can accept $\hstatei$ as the first party asserted it was correct, and the second party continued the application's execution instead of challenging it. 
Thus an honest party will always have a copy of the previous $\stateinfo$ to verify state transitions and issue challenges.

\paragraph{Motivation for turn-based commands} 
There are two motivations for the turn-based channel. 
First each party can submit a state assertion and the counterparty is always provided an opportunity to accept or challenge it. 
Second, each state assertion must strictly build upon a previously accepted state hash. 
If there are two or more state assertions that reference the same previous state hash, then $\chanblue$ can only accept one state assertion. 
Because of the requirement to strictly order state assertions and the need to `accept the first received state assertion', this lets an attacker simply pay a higher fee and front-run an honest party to ensure their state assertion is always accepted first (i.e. front-running ensures an honest party's state assertion is never accepted by $\chanblue$). 
Thus the turn-based nature of this state channel prevents the above front-running attack.

%\paragraph{Contract enforces the turn-based command} 
%It is always clear to the contract whose turn it is to assert a new state and we consider two cases. 
%If the assertin channel is instantiated, but the application's execution as not progressed off-chain, then it is always the first participant's turn. 
%Otherwise, both parties always explicitly acknowledge who should take the next turn when they are authorising a new state hash off-chain.
%Thus if one party submits  the latest state via $\chanblue.\setstateblue()$ before triggering a dispute, then the contract is informed whose turn is next.

\paragraph{Enforcing time-based events} 
The assertion channel is responsible for enforcing time-based events with the dispute period $\Delta$ and the application doesn't need to consider it. 
When the application is co-operatively progressing off-chain, an honest party will wait for a local timeout before triggering a dispute via the blockchain. 
For every new state assertion, the dispute process is reset to ensure each party has a time period of $\Delta$ to take their next move. 
If a party doesn't assert a new state before the deadline, then the honest party will notify the contract via $\chanblue.\timeoutblue()$.
This terminates the application and sends all coins (including the bonds) to the honest party.

\paragraph{Bond Requirement} 
Each party must deposit a bond to cover the cost of a successful challenge to their assertion. 
The bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$1.56 to approximately \$57 during network congestion.  
If the security bond isn't sufficient to challenge a state assertion, then the the counterparty may not challenge it.

\paragraph{Offline parties and PISA} 
There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
First, an attacker can trigger a dispute with the latest agreed state hash, and then assert an invaid state hash that benefits the attacker.
A watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner

\bibliographystyle{plain}
\bibliography{bib}

%\section{Conclusion}
%
%\paragraph{Acknowledgements} Chris Buckland and Patrick McCorry are supported by an Ethereum Foundation
%scaling grant, Ethereum Community Fund grant and a Research Institute grant.

\begin{figure}[H]
	\begin{boxedminipage}{\columnwidth}
		\begin{tabular}{l}
			\contract StateAssertionChannel \{ \\
			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\} \\
			\quad Status status; $\uintno$ deadline; $\hashblue$ hstate, $\uintno$ i; $\addr$ firstturn; \\ %\comment{// Latest state info}  \\
			\quad $\addr$ asserter; $\hashblue$ prevstate; $\bytes$ input; $\uintno$ cmd;\\
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_newstate) \{ \\
			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
			\quad \quad $\hashblue$ hmsg = hash(\_i, \_newstate,\_turn, $\addr(\this)$);  \\
			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
			\quad \quad status = Dispute.\ON; refundAllBonds(); \comment{// Cancel dispute and refund bonds} \\
			\quad \quad bestRound = \_i; hstate = \_newstate;  firstturn = \_turn; \comment{// Agreed state} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ triggerDispute() \{ \\
			\quad \quad $\require$(status == Status.ON \& onlyParties()); \\
			\quad \quad  status = Status.DISPUTE; \\
			\quad \quad deadline = now + disputePeriod; \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ assertState($\hashblue$ \_prevstate, $\hashblue$ \_newstate, $\bytes$ input, $\uintno$ cmd) \{ \\
			\quad \quad $\require$(status == Status.DISPUTE); \\
			\quad \quad $\require$(\_prevstate == hstate \&\& checkCallerTurn()) \\ 
			\quad \quad asserter = $\msgsender$; \comment{// Store name of asserter} \\ 
			\quad \quad prev\_hstate = \_prevstate; hstate = \_newstate; \\ 
			\quad \quad input = \_input; cmd = \_cmd; \\
			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
			\quad \}

		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
			\quad \quad \require(status == Status.DISPUTE); \\
			\quad \quad \require(asserter != $\msgsender$); \comment{// Stop self-challenging} \\
			\quad \quad \require(prev\_hstate == hash(\_oldstate)); \comment{// Verify old state is correct} \\
			\quad \quad $\hashblue$ temphstate = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \\ 
			\quad \quad $\ifs$(hstate != temphstate) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ timeOut() \{ \\
			\quad \quad \require(now $>=$ deadline \&\& status == Status.dispute); \\ 
			\quad \quad \comment{// Send all coins/bonds to asserter (i.e. last party to respond).} \\
			\quad \}
		\end{tabular}
		\\
		\\
		\\
		\begin{tabular}{l}
			\quad $\oninput$ resolve($\uintno$ balance1, $\uintno$ balance2) \{ \\
			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Let non-asserter challenge or resolve.} \\
			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
			\quad \quad \comment{// Send each party their final balance.} \\
			\quad \}
		\end{tabular}

	   	\begin{tabular}{l}
	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space} \\
	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\
	   		\quad $\oninput$ refundAllBonds() $\internal$; \comment{// Refunds all bonds} \\
	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\
	   		\}
	   \end{tabular}
	\end{boxedminipage}

	\caption{\label{fig:fallback} Example of the state assertion contract}
\end{figure}
\end{document}

### 2019-01-12 paper/main.tex
Added paper

--- 2019-01-12 paper/main copy.tex
@@
 			\contract StateAssertionChannel \{ \\
-			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\} \\
-			\quad Status status; $\uintno$ deadline; $\hashblue$ hstate, $\uintno$ i; $\addr$ firstturn; \\ %\comment{// Latest state info}  \\
-			\quad $\addr$ asserter; $\hashblue$ prevstate; $\bytes$ input; $\uintno$ cmd;\\
+			\quad $\enum$ Status \{$\DEPOSIT$, $\ON$, $\DISPUTE$\}, $\addr$[] plist; \\
+			\quad Status status; $\uintno$ deadline; $\hashblue$ $\hstatei$, $\uintno$ i; $\addr$ turn; \\ %\comment{// Latest state info}  \\
+			\quad $\addr$ asserter; $\hashblue$ $\hstateplus$; $\bytes$ input; $\uintno$ cmd; $\bool$ assertion; \\
 		\end{tabular}
@@
 		\begin{tabular}{l}
-			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_newstate) \{ \\
+			\quad $\oninput$ setstate($\bytes[]$ \_sigs, $\uintno$ \_i, $\addr$ \_turn, $\hashblue$ \_$\hstatei$) \{ \\
 			\quad \quad \require(\_i $>$ i)); \comment{ // Largest counter so far} \\
-			\quad \quad $\hashblue$ hmsg = hash(\_i, \_newstate,\_turn, $\addr(\this)$);  \\
+			\quad \quad $\hashblue$ hmsg = hash(\_i, \_$\hstatei$,\_turn, $\addr(\this)$);  \\
 			\quad \quad \require(verifySigs(hmsg, sigs, plist));  \comment{// Everyone signed new hstate} \\
-			\quad \quad status = Dispute.\ON; refundAllBonds(); \comment{// Cancel dispute and refund bonds} \\
-			\quad \quad bestRound = \_i; hstate = \_newstate;  firstturn = \_turn; \comment{// Agreed state} \\
+			\quad \quad delete(input,cmd,\hstateplus,asserter, assertion); \comment{// Delete assertion}\\
+			\quad \quad status = Status.\ON; i = \_i; $\hstatei$ = \_$\hstatei$;  turn = \_turn; \comment{// Agreed state} \\
 			\quad \}
@@
 			\quad $\oninput$ triggerDispute() \{ \\
-			\quad \quad $\require$(status == Status.ON \& onlyParties()); \\
-			\quad \quad  status = Status.DISPUTE; \\
-			\quad \quad deadline = now + disputePeriod; \\
+			\quad \quad $\require$(status == Status.ON \& onlyParties()); \comment{// Only parties trigger} \\
+			\quad \quad  status = Status.DISPUTE; deadline = now + disputePeriod;\\
 			\quad \}
@@
 		\begin{tabular}{l}
-			\quad $\oninput$ assertState($\hashblue$ \_prevstate, $\hashblue$ \_newstate, $\bytes$ input, $\uintno$ cmd) \{ \\
-			\quad \quad $\require$(status == Status.DISPUTE); \\
-			\quad \quad $\require$(\_prevstate == hstate \&\& checkCallerTurn()) \\ 
-			\quad \quad asserter = $\msgsender$; \comment{// Store name of asserter} \\ 
-			\quad \quad prev\_hstate = \_prevstate; hstate = \_newstate; \\ 
-			\quad \quad input = \_input; cmd = \_cmd; \\
+			\quad $\oninput$ assertState($\hashblue$ \_$\hstatei$, $\hashblue$ \_$\hstateplus$, $\bytes$ \_input, $\uintno$ \_cmd) \{ \\
+			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} checkCallerTurn()); \\
+			\quad \quad $\ifs($!assertion)  \{ \\ 
+			\quad \quad \quad assertion = true; $\require(\hstatei == \_\hstatei)$ \comment{// First assertion}  \\ 
+			\quad \quad \} $\elses$ \{ $\require$($\hstateplus$ == \_$\hstatei$); \} \comment{// Extending existing assertion} \\ 
+			\quad \quad asserter = $\msgsender$; input = \_input; cmd = \_cmd; \comment{// Store assertion} \\
+			\quad \quad $\hstatei$ = $\hstateplus$; $\hstateplus$ = \_$\hstateplus$; \comment{// i accepted. i+1 assertion} \\ 
 			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
@@
 			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
-			\quad \quad \require(status == Status.DISPUTE); \\
-			\quad \quad \require(asserter != $\msgsender$); \comment{// Stop self-challenging} \\
-			\quad \quad \require(prev\_hstate == hash(\_oldstate)); \comment{// Verify old state is correct} \\
-			\quad \quad $\hashblue$ temphstate = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \\ 
-			\quad \quad $\ifs$(hstate != temphstate) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
+			\quad \quad \require(status == Status.DISPUTE); \require(asserter != $\msgsender$);  \\
+			\quad \quad \require($\hstatei$ == hash(\_oldstate) AND assertion); \comment{// Assertion exists} \\
+			\quad \quad $\hashblue$ checkh = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
+			\quad \quad $\ifs$($\hstateplus$ != checkh) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
 			\quad \}
@@
 			\quad \quad $\ifs$(status == Status.Dispute) \{ \\
-			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Let non-asserter challenge or resolve.} \\
+			\quad \quad \quad $\require$(checkCallerTurn()); \comment{// Non-asserter must resolve b4 timeout.} \\
 			\quad \quad \} $\elses$ \{ \require(status == Status.ON); \} \comment{// No on-going dispute.} \\ 
 			\quad \quad $\require$(hstate == hash(balance1, balance2)); \comment{// Terminal state?} \\
-			\quad \quad \comment{// Send each party their final balance.} \\
+			\quad \quad \comment{// Send each party their final balance and bond.} \\
 			\quad \}
@@
 	   	\begin{tabular}{l}
-	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space} \\
+	   		\quad $\oninput$ deposit(); \comment{// Not implemented due to space - INCLUDES BOND} \\
 	   		\quad $\oninput$ onlyParties() $\returns(\bool)$; \comment{// Check if tx signer is whitelisted} \\

### 2019-01-12 paper/main_answers.tex
Added paper

j\PassOptionsToPackage{usenames}{xcolor}
\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass{llncs}
\usepackage[utf8]{inputenc}
\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{color}
\usepackage{boxedminipage}
\usepackage[ff,sets,keys,primitives,operators]{cryptocode}
\usepackage{framed}
\usepackage[group-separator={,}]{siunitx}
\newcommand\bmmax{2}
\usepackage{bm}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{footnote}
\usepackage{units}
\usepackage{multicol,lipsum}
\colorlet{iomsg}{MidnightBlue}
\colorlet{party}{brown}
\colorlet{entry}{NavyBlue}
\colorlet{string}{BlueViolet}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\instantiated}{\mathsf{instantiated}}
\newcommand{\instantiatedno}{\mathsf{NO}}
\newcommand{\instantiatedyes}{\mathsf{YES}}

\newcommand{\gamestatus}{\mathsf{phase}}
\newcommand{\gameregister}{\mathsf{INIT}}
\newcommand{\gamesetup}{\mathsf{SETUP}}
\newcommand{\gameattack}{\mathsf{ATTACK}}
\newcommand{\gamereveal}{\mathsf{REVEAL}}
\newcommand{\gamewinner}{\mathsf{WIN}}
\newcommand{\gamefraud}{\mathsf{FRAUD}}
\newcommand{\gamefinished}{\mathsf{GAMEOVER}}

\newcommand{\chanstatus}{\mathsf{status}}

\newcommand{\chanon}{\mathsf{ON}}
\newcommand{\chandispute}{\mathsf{DISPUTE}}
\newcommand{\chanoff}{\mathsf{OFF}}

\newcommand{\hready}{\mathsf{hready}}
\newcommand{\hboard}{\mathsf{hboard}}
\newcommand{\hcell}{\mathsf{hcell}}
\newcommand{\hship}{\mathsf{hship}}
\newcommand{\hshiplocation}{\mathsf{hshiplocation}}

%\newcommand{\hash}{\textsf{H}}
\newcommand{\cmd}{\mathsf{cmd}}
\newcommand{\hstate}{\mathsf{hstate}}
\newcommand{\hstatei}{\mathsf{hstate}_{\monotoniccounter}}
\newcommand{\hstateplus}{\ensuremath{\mathsf{hstate}_{\monotoniccounter+1}}}
\newcommand{\hstateminus}{\ensuremath{\mathsf{hstate}_{\monotoniccounter-1}}}
\newcommand{\monotoniccounter}{\mathsf{i}}
\newcommand{\stateinfo}{\mathsf{state}}
\newcommand{\stateinfoi}{\mathsf{state}_{\mathsf{i}}}
\newcommand{\stateinfominus}{\mathsf{state}_{\mathsf{i-1}}}
\newcommand{\stateinfoplus}{\mathsf{state}_{\mathsf{i+1}}}
\newcommand{\participant}{\mathcal{P}}

\newcommand{\rani}{\mathsf{r}_{\mathsf{i}}}
\newcommand{\ran}{\mathsf{r}}
\newcommand{\ranminus}{\mathsf{r}_{\mathsf{i-1}}}
\newcommand{\ranplus}{\mathsf{r}_{\mathsf{i+1}}}

\newcommand{\statechannel}{\mathsf{SC}}
\newcommand{\statechanneldispute}{\mathsf{SC}.\mathsf{trigger}}
\newcommand{\statechannelsetstate}{\mathsf{SC}.\mathsf{setstatehash}}
\newcommand{\statechannelresolve}{\mathsf{SC}.\mathsf{resolve}} 
\newcommand{\statechannelgetcommitment}{\mathsf{SC}.\mathsf{getstatehash}} 
\newcommand{\statechannelgetdispute}{\mathsf{SC}.\mathsf{getdispute}} 
\newcommand{\statechannelclose}{\mathsf{SC}.\mathsf{close}}

\newcommand{\sign}{\mathsf{Sign}}
\newcommand{\verifysig}{\mathsf{VerifySig}}

\newcommand{\battleship}{\mathsf{BS}}
\newcommand{\battleshipfraud}{\mathsf{BS.fraud}}
\newcommand{\battleshipattackcell}{\mathsf{BS.attackcell}}
\newcommand{\battleshipbegin}{\mathsf{BS.begingame}}
\newcommand{\battleshipquit}{\mathsf{BS.quitgame}}
\newcommand{\battleshipcommit}{\mathsf{BS.commit}}
\newcommand{\battleshipplacebet}{\mathsf{BS.placebet}}
\newcommand{\battleshipselectboard}{\mathsf{BS.select}}
\newcommand{\battleshiprevealcell}{\mathsf{BS.opencell}}
\newcommand{\battleshipsinking}{\mathsf{BS.sunk}}
\newcommand{\battleshiprevealships}{\mathsf{BS.openships}}
\newcommand{\battleshiprevealboard}{\mathsf{BS.openships}}
\newcommand{\battleshipgameover}{\mathsf{BS.gameover}}
\newcommand{\battleshipdeposit}{\mathsf{BS.deposit}}
\newcommand{\battleshipwithdraw}{\mathsf{BS.withdraw}}
\newcommand{\battleshipfinish}{\mathsf{BS.finish}}

%\newcommand{\battleshipshipnotplaced}{\mathsf{BS.fraudnothit}}
\newcommand{\battleshipdeclarednotsunk}{\mathsf{BS.declarednotsunk}}
\newcommand{\battleshipdeclarednothit}{\mathsf{BS.declarednothit}}
\newcommand{\battleshipsamecell}{\mathsf{BS.attacksamecell}}
\newcommand{\battleshiptwoships}{\mathsf{BS.celltwoships}}
\newcommand{\battleshipchallengeexpired}{\mathsf{BS.expiredchallenge}}

\newcommand{\battleshiplock}{\mathsf{BS.lock}}
\newcommand{\battleshipunlock}{\mathsf{BS.unlock}}
\newcommand{\battleshipgetstate}{\mathsf{BS.getstate}}

\newcommand{\appcontract}{\mathsf{AC}}
\newcommand{\applock}{\mathsf{AC.lock}}
\newcommand{\appunlock}{\mathsf{AC.unlock}}

\newcommand{\timerchallenge}{\mathsf{\Delta}_{\mathsf{challenge}}}
\newcommand{\timechallenge}{\mathsf{t}_{\mathsf{challenge}}}
\newcommand{\timerextra}{\mathsf{\Delta}_{\mathsf{extra}}}
\newcommand{\timerdispute}{\mathsf{\Delta}_{\mathsf{dispute}}}
\newcommand{\timenow}{\mathsf{t}_{\mathsf{now}}}
\newcommand{\timestart}{\mathsf{t}_{\mathsf{start}}}
\newcommand{\timeend}{\mathsf{t}_{\mathsf{end}}}
\newcommand{\timedispute}{\timenow + \mathsf{\Delta}_{\mathsf{dispute}}}

% Colorful diagrams 
\newcommand{\constructor}{\textcolor{entry}{\bf constructor }}
\newcommand{\oninput}{\textcolor{entry}{\bf function }}
\newcommand{\stringlitt}[1]{\texttt{\textcolor{string}{#1}}}

\begin{document}

	\title{Tutorial 1: Principles of Security Management}

	\author{Patrick McCorry}

	\institute{Kings College London, UK\\
		\email{patrick.mccorry@kcl.ac.uk}}

	\maketitle
	\begin{abstract}
	Exercises to understand the principles of security management. 
	It is recommended to make notes of discussions on this tutorial sheet for future use. 
	\end{abstract}

\section{Group of Appreciation of the Natterjack Toad (GANT)}

The Group of Appreciation of the Natterjack Toad (GANT) is a conservation group that is keen to promote and preserve the well-being of the Natterjack Toad. 
It is a UK-registered charity and has a significant number of members world-wide who are all keen to promote the work of GANT. 
%One fact about the natterjack toad, it is claimed to be Europe's noisiest amphibian with the male call being audiable over several kilometres. 
Unfortunately it is an endangered species that is gradulaly being destoryed by the development of new areas. 
For example, it was locally extinct in some areas of Wales due to development work and it had to be re-introduced.\footnote{https://www.denbighshirecountryside.org.uk/natterjack-toad/}

All information for the group can be accessed using a web-based application or by contacting the group's honorary secretary Dr Jane Peabody for the paper-based records. 
This information includes the group's member records, its activities, meeting places, natterjack toad habitats, confidential aspects about their work, etc. 
In the past, members have raised concerns about information assurance as the website has been previously compromised oweing to the server containing no significant security controls.

The chairman Ms Rachel Jackson has heard about information security and believes it is the right time to take it more seriously, but she doesn't know that much about it. 
This is where you come in. Ms Rachel Jackson has hired your group to learn more about protecting their information.

\subsection{What is Information Security?}

Let's get the ball rolling. 
You are preparing for a meeting with Ms Rachel Jackson to convince her that information security should be taken seriously by GANT.
In preparation for the meeting, your group should agree on the following principles and points:

\begin{itemize}
	\item What is Information Security?
	\item \textcolor{red}{The practice of preventing unauthorised access, use, disclosure, disruption, modification, inspection, recording or destruction of information}
	\item What is the focus of Information Security? 
	\item \textcolor{red}{Confidentiality, Integrity and Availability}
	\item What information assets under the control of GANT may require protection? 
	\item \textcolor{red}{Everything. This includes members records (i.e. date of birth, location, passwords), the toad's camp location (if leaked, people may attack them). etc}
\end{itemize}

It is also important to prepare a brief discussion about \textit{confidentiality vs availability} of information.
While they are conceptually opposing goals, you will need to convince Ms Rachel Jackson how there can be acceptable trade-offs for the two goals. 
Please use the informtion assets that you identified as part of the discussion.

\textcolor{red}{Confidentiality tries to keep information secret to only those who need to know, whereas availability seeks to make information accessible.  While information can be kept secret by removing all access to it, this raises the question whether it is then useful to keep at all. There must be a tradeoff to let only parties who need access to the information. Cryptography can be used encrypt the information so it can be accessible, but only those with the decryption key can open it. }

\section{What risks may GANT face in the future?}

The meeting with Ms Rachel Jackson has begun. 
She clearly understands the principles of Information Security, but she does not yet know how to assess threats, vulnerabilities or risk. 
To help her understand, identify three threats, vulnerabilities and risks that GANT's information assurance system needs to manage. 
Please remember that Ms Rachel Jackson is not tech savvy per say.
For example, she will not understand how a MYSQL injection attack works.
Try to use simple english to explain the above three points.

\textcolor{red}{A threat highlights a problem that if it arises will result in adverse consequences. This may include 1) Information about members might be accessible by unauthorised people. 2) Information about the habitats of the Natterjack toad might be used by those who are not inclined to support its ongoing existence. 3) The website might be comrpomised and unofficial messages added to it. }

\textcolor{red}{A vulnerability is a weakness in the system that might allow the threat to happen.  This may include 1) Records of members are stored in an unreliable computer system that may crash in the future. 2) Information about the toad's habitats may be stored on an old internet-based and insecure server. 3) The administrator password for the website has never been changed from the default password. }

\textcolor{red}{A risk is the consequence (and likelihood) of what may happen if the vulnerability is exploited. This may include 1) Unscrupulous property developers may gain access to personal details about members and later harass them. 2) A habitat of the Natterjack toad might be destroyed by someone who is not interested in its existence. 3) Someone might gain access to the GANT website and update it with offensive information.}

\section{Financially reasonable to pursue? }

You have helped increase Ms Rachel Jackson's awareness of dangers that may occur if there are no appropriate security controls in place.
During the discussion, she mentions that there may be times when implementing a security control is more expensive than the information asset that it is protecting. 
She is correct with this comment. 
Can you provide two examples of security controls that can be implemented for an information asset, but it may be cost-effective to do.

\textcolor{red}{Facial recognition to physical safe. Dr Jane Peabody keeps all records on paper and it would be nice if only her face could unlock a safe to access it. However, it is more cost-effective to use biometrics or just a physical key that she keeps.}

\textcolor{red}{Locking servers in a dedicated room. It is possible to keep the servers in a dedicated room and only Dr Jane Peabody has the key to access it. This is useful to prevent side-channel attacks etc but requires a room to be dedicated for this purpose. }

\section{Security culture and professionalism} 
While Ms Rachel Jackson is ready to prepare a budgetto implement an information security management system, she wants to ensure that all employees within the organisation takes it seriously. 
Again, she asks you for advice. 
What can she do to help promote security awareness within the organisation? And what are the likely benefits of a good security culture if it works?

\textcolor{Red}{\textbf{Training: } All employees should attend training (and hopefully fun) days about how to improve information assurance during their job. If they are properly informed about how to do it, then it should become part of the culture. }

\textcolor{Red}{\textbf{Senior Management Support: } Board members and all management should issue statements to all workers (and possibly publicly) about their commitment to information assurance. If the organisation is taking it seriously, then workers will understand its importance. }

\textcolor{Red}{\textbf{Security Champions: } Employees should be appointed as Security Champaigns across the organisation to be responsible for checking if policies are followed and reporting back any information assurance issues that arise. }

\textcolor{red}{The primary benefit of a good security culture is to reduce vulnerabilities being exploited by attacks. 
As well, it should help identify information assurance issues that arise as employees will feel their opinion matters and that they feel comfortable reporting it to senior management without fear of recourse. 
For example, if an employee's action led to an increased risk of a vulnerability, then it is best to report this early, rectify the issue and figure out how to prevent it happening again in the future.} 
\end{document}

### 2019-01-14 paper/main.tex
Added tests for measuring gas costs and refactored the channel contract to reduce costs of the assertState

@@
 	Furthermore it ensures an honest party will pay an approximate fixed cost to continue an application's execution via the dispute process. 
-	We provide a proof of concept implementation which demonstrates it costs approximately \$x to submit evidence  regardless of the smart contract's application.
+	We provide a proof of concept implementation which demonstrates it costs approximately \$0.02 to submit evidence  regardless of the smart contract's application.
 
@@
 
-%\paragraph{Proof of concept implementation} 
-%Table 1 outlines the gas costs for creating the state channel smart contract and its dispute process. 
-%As we can see creating the smart contract costs x, and the entire dispute process for a single state assertion costs x. 
-%
+\paragraph{Proof of concept implementation} 
+Our proof on concept implementation took 2,943,664 gas to deploy.
+Which  is approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127, the real world rate in January 2019.
+The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.
 
@@
 For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$1.56 to approximately \$57 during network congestion.  
-If the security bond isn't sufficient to challenge a state assertion, then the the counterparty may not challenge it.
+If the security bond isn't sufficient to challenge a state assertion, then the counterparty may not challenge it.
 
@@
 To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
-Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner
+Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner.
 

### 2019-01-14 test/stateAssertions.js

@@ -10,7 +10,7 @@ contract("StateAssertionChannel", async accounts => {
         const player1 = accounts[1];
         const bondAmount = 20;
         const StateAssertion = createGasProxy(StateAssertionChannel, gasLib, web3);
-        const channel = await StateAssertion.new(player0, player1, 10, accounts[2], bondAmount);        
+        const channel = await StateAssertion.new(player0, player1, 10, accounts[2], bondAmount);
 
         /// deposit ///
         const depositValue = 10;
@@ -23,14 +23,21 @@ contract("StateAssertionChannel", async accounts => {
         /// setstate ///
         const dummyHstate = "0x3456789873654523678728675367827445678765678765678987655665676567";
         const dummyRound = 1;
-        const dummyFirstTurn = player0;
+        const dummyFirstTurn = true;
         const player0Sig = sigTools.chopUpSig(
             await sigTools.hashAndSignState(dummyHstate, dummyRound, dummyFirstTurn, channel.address, player0)
         );
         const player1Sig = sigTools.chopUpSig(
             await sigTools.hashAndSignState(dummyHstate, dummyRound, dummyFirstTurn, channel.address, player1)
         );
-        const setStateResult = await channel.setstate([...player0Sig, ...player1Sig], dummyRound, dummyFirstTurn, dummyHstate, {from: player1});
+        const setStateResult = await channel.setstate(
+            [...player0Sig, ...player1Sig],
+            dummyRound,
+            dummyFirstTurn,
+            dummyHstate,
+
+            { from: player1 }
+        );
         assert.equal(setStateResult.logs[0].args["bestround"].toNumber(), dummyRound);
         assert.equal(setStateResult.logs[0].args["hstate"], dummyHstate);
 
@@ -38,8 +45,8 @@ contract("StateAssertionChannel", async accounts => {
         const state = "0xface";
         const dummyPrevState = sigTools.hashBytes(state);
         const dummyNewState = "0x3456789873654523678728675367827445678765678765678987655665676568";
-        let inputBytes = "0x"
-        for (let index = 0; index < 0; index++) {
+        let inputBytes = "0x";
+        for (let index = 0; index < 2; index++) {
             inputBytes += "5";
         }
 
@@ -48,16 +55,42 @@ contract("StateAssertionChannel", async accounts => {
 
         /// assert states ///
         const hashedBalances = sigTools.hashBalances(10, 10);
[…]

### 2019-01-14 paper/main.tex
Updated typos in paper pseudocode
Small updates and added sections for n-party and for implementation

@@
 
-	\title{2 Party State Assertion Channels }
+	\title{2 Party State Channels with State Assertions }
 
@@
 Cryptocurrencies do not scale.
-The community are pursing three approaches to alleviate the scalability issue which includes new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols.
-While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as it reduces  the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable.
+The community is pursing three approaches to alleviate the scalability issue.
+These are: new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols.
+While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as they reduce the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable.
 This paper focuses on the off-chain (or so-called Layer 2) approach that simply aims to reduce the network's load.
-One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of the global network. 
+One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of on the global network. 
 In the best case, the application is no longer restricted by the underlying blockchain's latency and all execution is free as it remains local between the parties. 
@@
 So far, there are two types of dispute processes for a state channel. 
-The first is a \emph{closure dispute} \cite{statechannelnetworks,battleship,celernetwork} as the dispute process is responsible for closing the channel, re-deploying the smart contract with the new state and letting parties continue its execution via the blockchain.
-The second is a \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual} as the dispute process collects commands from each party and then executes the command to compute the new state.
+The first is called \emph{closure dispute} \cite{statechannelnetworks,battleship,celernetwork} as the dispute process is responsible for closing the channel, re-deploying the smart contract with the new state and letting parties continue its execution via the blockchain.
+The second is called \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual,magmo} as the dispute process collects commands from each party and then executes the command to compute the new state.
 A recent case study empirically evaluated state channels as a scaling solution by building the  two player game battleship \cite{battleship}.
@@
 The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution).
+The case study also highlighted that as the application cannot be progressed withing the channel then, for liveness to be preserved, they would have to made on-chain.
+This could be expensive if the application required computationally complex progressions or if the number of transactions was high.
 We propose, \emph{State Assertion Channels}, which has a command-issuance dispute process\footnote{The assertion concept isn't compatible with closure channels as the full state is required to re-deploy an application.}.
@@
 \begin{itemize}
-	\item We propose the first state channel that ensures an honest party never pays the cost to send the applicaton's full state during the dispute proess.  
+	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
+	\item This state channel is also the first to make the cost of progressing the application as part of a dispute process independent of the computational complexity of the application, and instead just a function of the number of transactions made in progressing the application.
 	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
@@
 Briefly, one party submits the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
-Thi asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
+This asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
 Other interested parties can compute the transition locally to verify its validity.
@@
 If the challenge is successful, then the bond is used to refund the challenger. 
-Eigenmann, Moore and Johnson provided the first implementation of an optimistic contract for the Ethereum Name Service
+Eigenmann, Moore and Johnson provided the first demo implementation of an optimistic contract for the Ethereum Name Service
 \cite{optimisticcontracts}, but so far this technique has alluded real-world use.
@@
 \paragraph{Command Issuance State Channels}
-Sprites proposed the concept of a command-issuance state channel, and since then it has been extended by PISA \cite{mccorry2018pisa}, Counterfactual \cite{coleman2018counterfactual} and Magmo \cite{magmo}.
+Sprites proposed the concept of a command-issuance state channel, and since then it has been extended by PISA \cite{mccorry2018pisa}, Counterfactual \cite{counterfactual} and Magmo \cite{magmo}. 
 At a high level, one party can submit the latest $\stateinfoi$ agreed by all parties before triggering the dispute process.
@@
 \section{State Assertion Channels}
-We provide a high level overview of state assertion channels to show how it combines optimistic contracts and command issuance channels.
+We provide a high level overview of a state assertion channel to show how it combines optimistic contracts and command issuance channels.
 Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
@@
 If there is a disagreement off-chain, then both parties can continue its progression via the dispute process.
-Our contribution involves changing the dispute process to avoid sending the full application's state.
+Our contribution involves changing the dispute process to avoid sending the full application's state, and to avoid computing the next states on-chain.
 Instead parties will assert an application's new state by submitting a hash of the previous state $\hstatei$, the command $\cmd$, its $\inputs$, a hash of the next state $\hstateplus$ and a financial \texttt{bond}.
@@
 If the honest party successfully challenges an assertion and proves it is invalid, then they are sent the \texttt{bond} as a refund.
-Thus an honest party can always continue an applicaton's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.
+Thus an honest party can always continue an application's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.
 
@@
 \paragraph{Turn-based application} 
-We assume it is a turn-based application and each party performs their state transition in turn. 
+We assume it is a turn-based application and each party performs their state transition in turn until a terminal state is reached.
 As well, $\appblue$ must be instantiated on the blockchain to ensure its address is provided to the  state assertion contract $\chanblue$.
@@
 If there is a disagreement about a state transition, then one party can trigger a dispute which changes the status from $\ON \rightarrow \DISPUTE$.
-The contract self-enforces a turn-based dispute process.
-One party asserts a new state, and the other party can either challenge it by notifying the contract to check the state transition, or they can approve it by asserting a new state which extends it. 
-The dispute process can only finish and let the status change from $\DISPUTE \rightarrow \ON$ if one party submits a co-operatively signed new state.
+%The contract self-enforces a turn-based dispute process.
+%One party asserts a new state, and the other party can either challenge it by %notifying the contract to check the state transition, or they can approve it %by asserting a new state which extends it.
+%The dispute process can only finish and let the status change from $\DISPUTE %\rightarrow \ON$ if one party submits a co-operatively signed new state.
 
@@
 \paragraph{Proof of concept implementation} 
-Our proof on concept implementation took 2,943,664 gas to deploy.
-Which  is approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127, the real world rate in January 2019.
+We developed a proof of concept for the Ethereum blockchain.
+Our smart contract is written in Solidity\footnote{https://github.com/ethereum/solidity}, and gas costs were measured using Ganache\footnote{https://github.com/trufflesuite/ganache-cli}.
+The contract took 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which is the real world rate in January 2019.
 The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.
@@
 \paragraph{Enforcing time-based events} 
-The assertion channel is responsible for enforcing time-based events with the dispute period $\Delta$ and the application doesn't need to consider it. 
+The assertion channel is responsible for enforcing time-based events with the dispute period $\Delta$.
+% and the application doesn't need to consider it 
 When the application is co-operatively progressing off-chain, an honest party will wait for a local timeout before triggering a dispute via the blockchain. 
@@
 \paragraph{Offline parties and PISA} 
-There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
-First, an attacker can trigger a dispute with the latest agreed state hash, and then assert an invaid state hash that benefits the attacker.
-A watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
-Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
-To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
-Future work should consider whether the execution of an application can be delegated to a third party in an accountable manner.
+%There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
+It is possible for an attacker to trigger a dispute with the latest agreed state hash, and then assert an invalid state hash that benefits the attacker.
+Thus, if a party is offline and unable to challenge, an attacker can transition the channel to a state that was never agreed to by the party and does conform to a valid state transition.
+If the party uses a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and challenge, but this hinders state privacy.
+%Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
+%To prevent a timeout, the offline party must delegate the authority to continue the application's execution to the watching service.
+%Future work should consider whether the execution of an application can\ be delegated to a third party in an accountable manner.
+
+\paragraph{N-party state assertions}
+The state assertion paradigm can be extended to n-party state channels.
+To do so these channels would require that turns progress in a round-robin fashion, and that $\chanblue$ store the last \textbf{n} state assertions.
+This is so that a party can be sure that a state assertion will not be accepted unless they explicitly apply their own state assertion after it.
 
@@
 			\quad \quad deadline = now + disputePeriod; \comment{// Reset deadline after an assertion} \\
+			\quad \quad progressTurn()); \comment{// Increment the turn counter} \\
 			\quad \}
@@
 			\quad $\oninput$ challengeAssertion($\bytes$ \_oldstate) \{ \\
-			\quad \quad \require(status == Status.DISPUTE); \require(asserter != $\msgsender$);  \\
+			\quad \quad $\require$(status == Status.DISPUTE \texttt{AND} 		checkCallerTurn()); \\
 			\quad \quad \require($\hstatei$ == hash(\_oldstate) AND assertion); \comment{// Assertion exists} \\
-			\quad \quad $\hashblue$ checkh = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
+			\quad \quad $\hashblue$ check = $\appblue.\transitionblue$(asserter, \_oldstate, input, cmd); \comment{// Compute} \\ 
 			\quad \quad $\ifs$($\hstateplus$ != checkh) \{ \comment{// Send all coins and bond to non-cheater.}  \} \\
@@
 	   		\quad $\oninput$ checkCallerTurn() $\returns$($\bool$); \comment{Enforce turn based disputes} \\
+	   		\quad $\oninput$ progressTurn() $\returns$($\bool$); \comment{Update the turn counter} \\
 	   		\quad $\oninput$ verifySigs($\bytes$ hmsg, $\bytes[]$ sigs, $\addr[]$ signers) $\returns(\bool)$; \\

### 2019-01-14 paper/main.tex
Updatets to paper based on patrick's feedback

@@
 We developed a proof of concept for the Ethereum blockchain.
-Our smart contract is written in Solidity\footnote{https://github.com/ethereum/solidity}, and gas costs were measured using Ganache\footnote{https://github.com/trufflesuite/ganache-cli}.
-The contract took 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which is the real world rate in January 2019.
+Our smart contract is written in Solidity\footnote{https://pastebin.com/UBVvZ0FU}, and gas costs were measured using a private network.
+The assertions contract costs 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which is the real world rate in January 2019.
 The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.
@@
 %There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
-It is possible for an attacker to trigger a dispute with the latest agreed state hash, and then assert an invalid state hash that benefits the attacker.
-Thus, if a party is offline and unable to challenge, an attacker can transition the channel to a state that was never agreed to by the party and does conform to a valid state transition.
-If the party uses a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and challenge, but this hinders state privacy.
+If a party is offline (and thus unable to challenge), then the counterparty can trigger a dispute with the latest agreed hash and then assert an invalid state hash that benefits the attacker (i.e.
+send them all the coins).
+If a party relies a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
 %Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
@@
 
-\paragraph{N-party state assertions}
-The state assertion paradigm can be extended to n-party state channels.
-To do so these channels would require that turns progress in a round-robin fashion, and that $\chanblue$ store the last \textbf{n} state assertions.
+\paragraph{Extending to N-parties}
+Future work should investigate how the state assertion paradigm could be extended to n-party state channels.
+Channels could progress in a round-robin fashion and store the last \textbf{n} state assertions.
 This is so that a party can be sure that a state assertion will not be accepted unless they explicitly apply their own state assertion after it.

### 2019-01-14 paper/main.tex
Small touch up to poc section

@@
 
-	\title{2 Party State Channels with State Assertions }
+	\title{Two-Party State Channels with State Assertions }
 
@@
 	An empirical case study to evaluate state channels as a scaling solution for cryptocurrencies demonstrated that providing an application's full state during the dispute process for a state channel is financially costly (i.e.
-\$1.5 to \$57.57 for a battleship game) which can hamper their real-world use.
+\$0.24 to \$8.83 for a battleship game) which can hamper their real-world use.
 	To overcome this issue, we present \emph{State Assertion Channels}, the first state channel to guarantee  an honest party is always refunded the cost if it becomes necessary to send an application's full state during the dispute process.
@@
 They highlighted the most expensive aspect of any dispute process is sending the application's full state. 
-For example, the  case study claimed that sending the full game state approximately costs \$1.57 when the blockchain is not congested, but it can potentially sky-rocket to \$57.57 if the blockchain is congested.
+For example, the  case study claimed that sending the full game state approximately costs \$0.24 when the blockchain is not congested, but it can potentially sky-rocket to \$8.83 if the blockchain is congested.
 The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution).
@@
 Our smart contract is written in Solidity\footnote{https://pastebin.com/UBVvZ0FU}, and gas costs were measured using a private network.
-The assertions contract costs 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which is the real world rate in January 2019.
-The cost to make a state assertion is 59,774+39.5n gas (\$0.02), where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.
+The assertions contract costs 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which was the real world rate in January 2019.
+The cost to make a state assertion is only 59,774+39.5n gas (\$0.02 at 2.6 Gwei and \$0.77 on a congested network at 96 Gwei) where \textit{n} corresponds to the number of bytes supplied as $\inputs$ to the assertion.
+Compared to the 725,508 gas (\$0.24 at 2.6 Gwei and \$8.83 at 96 Gwei) required to send the full battleship state.
 
@@
 %Thus the honest party must have the previous state in plaintext as they must verify the state transition before accepting it.
-The first opportunity requires one party to submit the state hash via $\chanblue.\setstateblue()$ which requires both parties to have already signed it. 
-The second opportunity requires one party to submit $\hstatei$ via $\chanblue.\assertstate()$ and for the honest party to continue the application's execution by asserting the next $\hstateplus$ via $\chanblue.\assertstate()$.
-The contract can accept $\hstatei$ as the first party asserted it was correct, and the second party continued the application's execution instead of challenging it. 
+The first requires one party to submit the state hash via $\chanblue.\setstateblue()$ which requires both parties to have already signed it. 
+The second requires one party to submit $\hstatei$ via $\chanblue.\assertstate()$ and for the honest party to continue the application's execution by asserting the next $\hstateplus$ via $\chanblue.\assertstate()$.
+The contract can accept $\hstatei$ as the first party asserted it was correct, and the second party continued execution instead of challenging $\hstatei$. 
 Thus an honest party will always have a copy of the previous $\stateinfo$ to verify state transitions and issue challenges.
@@
 The bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
-For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$1.56 to approximately \$57 during network congestion.  
+For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$0.24 to approximately \$8.83 during network congestion.  
 If the security bond isn't sufficient to challenge a state assertion, then the counterparty may not challenge it.

### 2019-01-14 paper/main.tex
Added email and updated contributions

@@
 	\institute{Kings College London, UK\\
-		\email{patrick.mccorry@kcl.ac.uk}}
+		\email{cpbuckland88@gmail.com}
+		\email{patrick.mccorry@kcl.ac.uk}
+	}
 
@@
 	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
-	\item This state channel is also the first to make the cost of progressing the application as part of a dispute process independent of the computational complexity of the application, and instead just a function of the number of transactions made in progressing the application.
+	\item Our state channel is also the first to ensure the cost of progressing an application is based only the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
 	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 

### 2019-01-14 paper/main.tex
Missing 'on'

@@
 	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
-	\item Our state channel is also the first to ensure the cost of progressing an application is based only the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
+	\item Our state channel is also the first to ensure the cost of progressing an application is based only on the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
 	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 

### 2019-02-01 paper/main.tex
Update main.tex

@@
 
-	\title{Two-Party State Channels with State Assertions }
+	\title{Two-Party State Channels with Assertions }
 
@@
 	Furthermore it ensures an honest party will pay an approximate fixed cost to continue an application's execution via the dispute process. 
-	We provide a proof of concept implementation which demonstrates it costs approximately \$0.02 to submit evidence  regardless of the smart contract's application.
+	We provide a proof of concept implementation in Ethereum which demonstrates it costs approximately \$0.02 to submit evidence  regardless of the smart contract's application.
 
@@
 
-Cryptocurrencies do not scale.
+Blockchain-based cryptocurrencies do not scale.
 The community is pursing three approaches to alleviate the scalability issue.
-These are: new blockchain protocols \cite{bano2017consensus}, sharding transactions into distinct processing areas and off-chain protocols.
-While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as they reduce the diversity of peers with the computatonal, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miner's accountable.
+These are: new blockchain protocols \cite{bano2017consensus,sompolinsky2016spectre,eyal2016bitcoin}, sharding transactions into distinct processing areas \cite{al2017chainspace,kokoris2018omniledger,luu2016secure} and off-chain protocols \cite{battleship,counterfactual,celernetwork,decker2015fast,poon2016bitcoin,poon2017plasma,khalil2018nocust}.
+While the first two approaches can strictly increase the network's throughput, they harm the network's public verifiability as they reduce the diversity of peers with the computational, bandwidth or storage requirements to validate all transactions on the network and ultimately hold the miners accountable.
+\cite{gervais2016security,croman2016scaling}
 This paper focuses on the off-chain (or so-called Layer 2) approach that simply aims to reduce the network's load.
+
 One promiment off-chain approach are state channels that lets a group of parties process transactions (and execute a smart contract) locally amongst themselves instead of on the global network. 
@@
 The second is called \emph{command-issuance dispute} \cite{miller2017sprites,mccorry2018pisa,counterfactual,magmo} as the dispute process collects commands from each party and then executes the command to compute the new state.
+
 A recent case study empirically evaluated state channels as a scaling solution by building the  two player game battleship \cite{battleship}.
-They highlighted the most expensive aspect of any dispute process is sending the application's full state. 
+It highlights that sending the application's full state during the dispute process can be financially expensive which may deter real-world use of state channels. 
 For example, the  case study claimed that sending the full game state approximately costs \$0.24 when the blockchain is not congested, but it can potentially sky-rocket to \$8.83 if the blockchain is congested.
-The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too clostly (and thus they cannot self-enforce the application's correct execution).
-The case study also highlighted that as the application cannot be progressed withing the channel then, for liveness to be preserved, they would have to made on-chain.
-This could be expensive if the application required computationally complex progressions or if the number of transactions was high.
-We propose, \emph{State Assertion Channels}, which has a command-issuance dispute process\footnote{The assertion concept isn't compatible with closure channels as the full state is required to re-deploy an application.}.
-and overcomes the issue of sending the application's full state by leveraging the concept of an optimistic contract.
+The above can clearly hamper real-world use of state channels as an honest party will not use the dispute process if it is too costly (and thus they cannot self-enforce the application's correct execution).
+The case study also highlights the need to preserve liveness of an application.
+If one party is no longer co-operating off-chain, then a state channel should ensure the application's progress can continue via the blockchain.
+Again, this can be costly if progressing the application is computationally expensive or if it requires a significant number of transactions.
+
+To alleivate the above issues, we propose \emph{State Assertion Channels}.
+It builds upon state channels with command-issuance disputes and relies on the concept of an optimistic Combined, honest parties can always assert the hash of a new state (and thus progress an application's execution) without the blockchain computing the state transition directly.
 Our contributions:
@@
 
-An optimistic smart contract trades the cost of computation with time.
+An optimistic smart contract trades the cost of computation for time.
 This lets a smart contract accept an application's new state if no one has proved it is invalid within a fixed challenge period. 
-Briefly, one party submits the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
+Briefly, one party submits to the optimistic smart contract the application's $\stateinfoi$, a command $\cmd$, its $\inputs$, the next $\stateinfoplus$ and a financial bond. 
 This asserts that $\stateinfoplus$ is the next state if the smart contract were to compute  $\stateinfoplus = \texttt{Transition}(\stateinfoi, \cmd, \inputs)$. 
@@
 If the asserted state is invalid, then anyone can issue a challenge by notifying the smart contract to compute the transition.
-If the challenge is successful, then the bond is used to refund the challenger. 
+If the challenge is successful, then a bond is used to refund the challenger. 
 Eigenmann, Moore and Johnson provided the first demo implementation of an optimistic contract for the Ethereum Name Service
@@
 \section{State Assertion Channels}
-We provide a high level overview of a state assertion channel to show how it combines optimistic contracts and command issuance channels.
-Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
-Finally we'll present the state assertion channel contract $\chanblue$ and the interaction amongst both parties, $\chanblue$ and $\appblue$.
+%We provide a high level overview of a state assertion channel to show how it combines optimistic contracts and command issuance channels.
+%Afterwards we'll provide a list of assumptions for the application contract $\appblue$ to ensure new assertions can always be challenged. 
+%Finally we'll present the state assertion channel contract $\chanblue$ and the interaction amongst both parties, $\chanblue$ and $\appblue$.
 
-\subsection{High level overview}
+%\subsection{High level overview}
 
 The state assertion contract $\chanblue$ and the application contract $\appblue$ must be deployed on the blockchain.
-Each party must lock coins into the state channel before they can begin co-operatively executing the application off-chain amongst themselves. 
+Each party must lock coins into the state assertion contract before the state channel is activated.
+Both parties can co-operatively execute the application off-chain amongst themselves by executing every state transition for $\appblue$ locally and exchanging signatures for every new state. 
 If there is a disagreement off-chain, then both parties can continue its progression via the dispute process.
+
 Our contribution involves changing the dispute process to avoid sending the full application's state, and to avoid computing the next states on-chain.
@@
 If the honest party successfully challenges an assertion and proves it is invalid, then they are sent the \texttt{bond} as a refund.
-Thus an honest party can always continue an application's execution by asserting a hash of the next state, and they are always refunded the cost of challenging an invalid assertion.
+
+Thus an honest party can always continue an application's execution via the blockchain's dispute process by asserting a hash of the next state.
+As well, they are always refunded the cost of sending the application's full state in order to challenge an invalid state assertion.
 
@@
 \paragraph{Turn-based application} 
-We assume it is a turn-based application and each party performs their state transition in turn until a terminal state is reached.
+We assume that the parties execute a turn-based application where each party performs their state transition in turn until a terminal state is reached.
 As well, $\appblue$ must be instantiated on the blockchain to ensure its address is provided to the  state assertion contract $\chanblue$.
@@
 $	\hstateplus := \texttt{Transition}(\stateinfoi, \cmd, \inputs); $.
-The application contract is stateless and the state must be supplied to compute a state transition.
+The application contract is stateless consequently the state must be supplied to compute a state transition.
 
 \paragraph{No exceptions or out-of-gas errors} 
-The application's transition function must return a hash of the state $\hstate$.
-If the command doesn't exist or its execution simply fails, then it should return $\hstate = 0$. 
-This ensures $\chanblue$ can always verify a state assertion's validity.
-If out-of-gas exceptions were permitted by an application, then it can be leveraged to prevent an honest user challenging it (i.e. $\chanblue.\chanchallenge()$'s execution will never complete).
+ In Ethereum, an entire transaction's execution can be reverted if a smart contract throws an exception (i.e. out of gas). 
+If the application $\appblue$ can throw an exception, then it can be used to revert the execution of an honest party's challenge. 
+Thus the application's transition function should not permit exceptions.
+We propose the transition function should return $\hstate$ and if the command doesn't exist or its execution simply fails, then it should return $\hstate = 0$. 
+This ensures an honest party can always issue a challenge via $\chanblue.\chanchallenge()$ as the state transition (and the verification) will always complete its execution.
 
@@
 \paragraph{Triggering a dispute} 
-In general, a dispute must be triggered if the counterparty stops honestly following the protocol (i.e. aborts and stops responding) and there are two cases to consider.
+In general, a dispute must be triggered if the counterparty stops responding in the state channel (i.e. they do not agree with the state update and they refuse to sign it). 
+There are two cases to consider. 
 Either the proposer is waiting on a signature from the verifier to authorise the new state, or the verifier is waiting on the proposer to propose a new state transition. 
@@
 We developed a proof of concept for the Ethereum blockchain.
-Our smart contract is written in Solidity\footnote{https://pastebin.com/UBVvZ0FU}, and gas costs were measured using a private network.
+Our smart contract is written in Solidity\footnote{Our PoC is an optimised for Solidity https://pastebin.com/UBVvZ0FU}, and gas costs were measured using a private network.
 The assertions contract costs 2,943,664 gas to deploy, approximately \$0.97 using the gas price of 2.6 Gwei and the conversion rate of 1 ether = \$127 which was the real world rate in January 2019.
@@
 
-\paragraph{Honest party can always verify a state transition} 
-%An honest party can only challenge a state assertion if they have a copy of the previous $\stateinfo$.
-There are only two opportunities for a new state hash to be accepted by $\chanblue$. 
+\paragraph{Honest party can always verify state assertions} 
+To issue a challenge or continue the application's execution, an honest party must have the $\stateinfoi$ which corresponding to the contract's accepted $\hstatei$.
+%An honest party can only challenge a state assertion if they have a copy of the previous $\stateinfo$.]
+There are only two situations when a new $\hstatei$ can be accepted by $\chanblue$.
+% in both situations the honest party will always have knowledge of $\stateinfoi$. 
 %Thus the honest party must have the previous state in plaintext as they must verify the state transition before accepting it.
-The first requires one party to submit the state hash via $\chanblue.\setstateblue()$ which requires both parties to have already signed it. 
-The second requires one party to submit $\hstatei$ via $\chanblue.\assertstate()$ and for the honest party to continue the application's execution by asserting the next $\hstateplus$ via $\chanblue.\assertstate()$.
-The contract can accept $\hstatei$ as the first party asserted it was correct, and the second party continued execution instead of challenging $\hstatei$. 
-Thus an honest party will always have a copy of the previous $\stateinfo$ to verify state transitions and issue challenges.
+In the first situation, $\hstatei$ will be accepted by $\chanblue$ if it is submitted using $\chanblue.\setstateblue()$, but this requires both parties to have already signed it (and thus acknowledge they know $\stateinfoi$).
+In the second situation, a new $\hstatei$ will be accepted by $\chanblue$ if the counterparty has asserted it using $\chanblue.\assertstate()$ and if the honest party continues the application's execution by asserting the next $\hstateplus$ via $\chanblue.\assertstate()$.
+We highlight the contract accepts $\hstatei$ as the honest party has countinued its execution instead of challenging it. 
+As the above demonstrates, an honest party will always have a copy of $\stateinfoi$ if the corresponding $\hstatei$ is accepted by the contract.
+Thus they can always verify state transitions and issue challenges.
 
@@
 Each party must deposit a bond to cover the cost of a successful challenge to their assertion. 
-The bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
+A bond's value must consider the worst-case when a transaction fee spikes due to network congestion. 
 For example, in the battleship empirical case study it was highlighted that submitting the game's state can sky rocket from \$0.24 to approximately \$8.83 during network congestion.  
@@
 %There are two issues for a watching service like PISA \cite{mccorry2018pisa} to protect the channel. 
-If a party is offline (and thus unable to challenge), then the counterparty can trigger a dispute with the latest agreed hash and then assert an invalid state hash that benefits the attacker (i.e.
-send them all the coins).
-If a party relies a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge, but this hinders state privacy.
+If the honest party is offline, then the counterparty can trigger a dispute with the latest agreed hash and then assert an invalid state hash (i.e.
+sends the counterparty all the coins in the channel).
+If the offline party relies on a watching service, like PISA \cite{mccorry2018pisa}, then the watching service must have a copy of the latest state in plaintext to verify the invalid state transition and issue a challenge.
+This hinders state privacy as the watching service can view the channel's internal state. 
+As well, a watching service cannot perform a valid state transition on the offline party's behalf, so the offline party must ensure the only valid state transition for the counterparty is the application's terminal state.
+
 %Second, an attacker can issue a new state assertion and claim all coins after the deadline using $\chanblue.\timeoutblue()$. 
@@
 
+\section{Acknowledgements} Chris Buckland and Patrick McCorry are supported by an Ethereum Foundation
+scaling grant, Ethereum Community Fund grant and a Research Institute grant.
+
 \bibliographystyle{plain}
@@
 %
-%\paragraph{Acknowledgements} Chris Buckland and Patrick McCorry are supported by an Ethereum Foundation
-%scaling grant, Ethereum Community Fund grant and a Research Institute grant.
 
